Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
brush up the Haddock explanation.

As we described, Haddock version 2.7.2 or earlier provides markup syntax for
code blocks, but does not provide any markup syntax for evidence.
We implemented markup support for examples ({\tt >>>}) and it is available in
Haddock version 2.8 or later.
We also extended Haddock to support markup for properties ({\tt prop>}) which
will be available with a future release of Haddock.
Both examples and properties in Haddock comments are pretty-printed when
generating documentation, (e.g. as HTML).

>>>>

Haddock version 2.7.2 or earlier provided markup syntax for
code blocks, but did not provide any markup syntax for evidence.
As we described, we implemented markup support for examples ({\tt >>>}) in 2010.
It is available in Haddock version 2.8 or later.
We also extended Haddock to support markup for properties ({\tt prop>}) which
will be available with a future release of Haddock.
Both examples and properties in Haddock comments are pretty-printed when
generating documentation, (e.g. as HTML).
